Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-29 Paper/chokepoint.tex
updates to equations

Given a set of routing trees\Ben[inline]{paths?}, chokepoint potential is an intuitive way to
compare individual ASes. With this measure, the sum of the chokepoint potential
for all border ASes for a country is 1.0, as in, all of the border ASes
collectively control the flow of information over the nation's border. We
define the aggregate \emph{national chokepoint potential} as the number of
border ASes required to control a particular fraction $f$ of paths. Formally,
given a country,$c$, with a set of $k$ border ASes $\{a_1,a_2,\cdots,a_k\}$ with
$cp(a_i)>cp(a_j) \forall i<k$ (i.e.\ sorted in descending order), the
we find the smallest $j$ such that

>>>>

Given a set of routing trees\Ben[inline]{paths?}, chokepoint potential is an intuitive way to
compare individual ASes. With this measure, the sum of the chokepoint potential
for all border ASes for a country is 1.0, as in, all of the border ASes
collectively control the flow of information over the nation's border. We
define the aggregate \emph{national chokepoint potential} as the number of
border ASes required to control a particular fraction $f$ of paths. Formally,
given a country,$c$, with a set of $k$ border ASes $\{a_1,a_2,\cdots,a_k\}$ with
$cp(a_i)>cp(a_j) \forall i<j$ (i.e.\ sorted in descending order), the
we find the smallest $j$ such that
